\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-11-20 Documentation/Replication_Instruction.tex
final submission

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper. For more information on the NGSPS, please visit the following websites: \url{http://env.people.com.cn/GB/8220/113963/index.html}, or \url{http://www.mee.gov.cn/home/ztbd/rdzl/wrypc/}.\footnote{The latter website was initially dedicated to the first NGSPS starting in 2007. Since the launch of the second NGSPS in 2017, the content of the website has been changed accordingly. However, the two surveys share similar structures.} The urls were retrieved on November 15th, 2019 and may vary in the future.
    \item
    The CNEC was conducted by the National Bureau of Statistics (NBS) of China in 2004, and was designed to cover the entire population of Chinese firms in that year. The firm-level data from the CNEC are not available to the general public and therefore not uploaded as part of our data files. For data access, please contact the NBS of China at \url{wgsjsys@stats.gov.cn}. For more information on the CNEC, please visit the dedicated page maintained by NBS at the following url: \url{http://www.stats.gov.cn/ztjc/zdtjgz/zgjjpc}. The url was retrieved on November 15th, 2019 and may vary in the future.
   % The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University. \\ \rtext{MORE INFORMATION IS NEEDED HERE!!!!!!!!}
    \item
    The SUSB is publicly available from the U.S. Census Bureau's dedicated website. The url, retrieved on November 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

@@

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}
Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files. Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which results; the datasets are referenced using the above two-letter acronyms.

@@

    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.\footnote{The code snippet \textit{must be} executed by using the MATLAB shortcut of 'Select $\rightarrow$ F9'. Executing \bcode{misc.m} by using the \textit{Run} command in MATLAB toolstrip would yield an error when calling the function \code{plot}. This is confirmed to be a known issue by staff from MathWorks. The supporting team claims that the issue has been fixed in MATLAB R2019b. We were not able to test the code under the environment.} The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    \item
    Several calibration targets are computed from the data as well. This last bulletin point explains where they are computed.
    \begin{itemize}
        \item
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        \item
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        \item
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        \item
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}
\end{enumerate}

>>>>

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper. For more information on the NGSPS, please visit the following websites: \url{http://env.people.com.cn/GB/8220/113963/index.html}, or \url{http://www.mee.gov.cn/home/ztbd/rdzl/wrypc/}.\footnote{The latter website was initially dedicated to the first NGSPS starting in 2007. Since the launch of the second NGSPS in 2017, the content of the website has been changed accordingly. However, the two surveys share similar structures.} The urls were retrieved on November 15th, 2019 and may vary in the future.
    \item
    The CNEC was conducted by the National Bureau of Statistics (NBS) of China in 2004, and was designed to cover the entire population of Chinese firms in that year. The firm-level data from the CNEC are not available to the general public and therefore not uploaded as part of our data files. For data access, please contact the NBS of China at \code{wgsjsys@stats.gov.cn}. For more information on the CNEC, please visit the dedicated page maintained by NBS at the following url: \url{http://www.stats.gov.cn/ztjc/zdtjgz/zgjjpc}. The url was retrieved on November 15th, 2019 and may vary in the future.
   % The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University. \\ \rtext{MORE INFORMATION IS NEEDED HERE!!!!!!!!}
    \item
    The SUSB is publicly available from the U.S. Census Bureau's dedicated website. The url, retrieved on November 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

@@

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}
Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files. Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which result; the datasets are referenced using the above two-letter acronyms.

@@

    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.\footnote{The code snippet \textit{must be} executed by using the MATLAB shortcut of 'Select $\rightarrow$ F9' unless version 2019b is used. Executing \bcode{misc.m} by using the \textit{Run} command in MATLAB toolstrip would yield an error when calling the function \code{plot}. This is confirmed to be an issue by staff from MathWorks. The supporting team informed us that the issue has been fixed in MATLAB R2019b. We were not able to test the code under the environment.} The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    \item
    Several calibration targets are computed from the data as well. This last bulletin point explains where they are computed.
    \begin{itemize}
        \item
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        \item
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        \item
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        \item
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}
\end{enumerate}
